This is an example of article title

### 2019-06-02 paper/paper.tex
jl

The {\tt sort\_net} generated function expects elements to which {\tt max} and {\tt min} are defined. It can be called with simple data types, {\em e.g.} {\tt sort\_net(4,2,5,3)} works. In practice \chipsort often calls this function with vectors, completely relying on SIMD.jl~\cite{erik_schnetter_2019_2592633}. This module maps a vector in Julia similar to tuples or static arrays straight to LLVM vector types, ensuring SIMD code can be produced when possible and also allowing the flexibility of handling logic vectors that are larger than the actual registers, or spilling data to the stack if all registers are occupied.

@@

\subsection{Other languages}
A simple experiment was also carried out with different programming languages in the same machine, and with Julia in different machines to provide a richer context. Table~\ref{tab:bench-cxx} displays statistics collected from Julia, Python and C++ programs. For the case of Python the measurements obtained by calling the function through PyCall were better than using the native Python shell, therefore the best value was kept. Results obtained for C++ with Julia inter-operation using Cxx.jl were slightly worse than native, thus discarded. While Numpy was almost as fast as Julia, no reason could be found for the dismal performance of the C++ standard library.

@@

While the main \chipsort method relies on compiler optimizations, other methods utilize explicit vectorization trough SIMD.jl. \chipsort makes extensive use of metaprogramming, more specifically Julia generated functions. This allows functions like sorting networks to be implemented in an abstract and generic way. The networks are represented as data structures, used by a higher-level program to assemble the final network code. This contrasts with other libraries where different networks are implemented straight as final functions. Julia also has the opportunity to perform custom optimizations since \chipsort is implemented in pure Julia with abstract methods that can be specialized.

>>>>

The {\tt sort\_net} generated function expects elements to which {\tt max} and {\tt min} are defined. It can be called with simple data types, {\em e.g.} {\tt sort\_net(4,2,5,3)} works. In practice \chipsort often calls this function with vectors, completely relying on {\tt SIMD.jl}~\cite{erik_schnetter_2019_2592633}. This module maps a vector in Julia similar to tuples or static arrays straight to LLVM vector types, ensuring SIMD code can be produced when possible and also allowing the flexibility of handling logic vectors that are larger than the actual registers, or spilling data to the stack if all registers are occupied.

@@

\subsection{Other languages}
A simple experiment was also carried out with different programming languages in the same machine, and with Julia in different machines to provide a richer context. Table~\ref{tab:bench-cxx} displays statistics collected from Julia, Python and C++ programs. For the case of Python the measurements obtained by calling the function through PyCall were better than using the native Python shell, therefore the best value was kept. Results obtained for C++ with Julia inter-operation using {\tt Cxx.jl} were slightly worse than native, thus discarded. While Numpy was almost as fast as Julia, no reason could be found for the dismal performance of the C++ standard library.

@@

While the main \chipsort method relies on compiler optimizations, other methods utilize explicit vectorization trough {\tt SIMD.jl}. \chipsort makes extensive use of metaprogramming, more specifically Julia generated functions. This allows functions like sorting networks to be implemented in an abstract and generic way. The networks are represented as data structures, used by a higher-level program to assemble the final network code. This contrasts with other libraries where different networks are implemented straight as final functions. Julia also has the opportunity to perform custom optimizations since \chipsort is implemented in pure Julia with abstract methods that can be specialized.
